---
output:
  word_document: default
  html_document: default
---
# Module 3-Assignment 1
## Rivera, Katerina 
### Data Visualization 

I will be using datasets containing candy rankings and candy production to complete this document. 
```{r}
library(tidyverse)
candy_data <- read_csv("candy_data.csv")
candy_production <- read_csv("candy_production.csv")
```

#### Visualization with Scatterplots (geom_point)
```{r}
ggplot(data=candy_data, aes(x=sugarpercent, y=pricepercent)) +
  geom_point() +
  geom_smooth(method = "lm") +
  geom_text(check_overlap = T, vjust = "bottom", nudge_y = 0.01, angle = 30, size = 2, aes(label=competitorname)) +
  labs(title = "Sugar by Price Scatterplot", x = "Sugar content (percentile", y = "Price (percentile)")
```

From this data, we can conclude that RootBeer Barrels and Dum Dum's had the highest sugar content with lowest price. Milky Way Simply Caramel is the highest in both sugar content and price. 

#### Line Chart of Candy Production 

Below we have used the candy production dataset that will display a specific date and how production during that month is compared to 2012. 

```{r}
ggplot(data=candy_production, aes(x=observation_date, y=IPG3113N, group=1)) +
  geom_line() + 
  geom_smooth() + 
  labs(title = "Monthly Candy Production", x = "Year", y = "As percent of 2012 production")
```

#### Bar Chart of Ingredients 
```{r}
ggplot() +
  geom_bar(data=candy_data, aes(chocolate))
```
```{r}
candyFeatures <- candy_data %>% select(2:10)
candyFeatures[] <- lapply(candyFeatures, as.logical)
ggplot() +
  geom_bar(data=candyFeatures, aes(chocolate))
```

